MINOS Handover Plots

### 2024-02-07 minos/validation/handovers.Rmd
Testing PCS with different model types (currently RandomForest), and added some diagnostic histograms and density plots in handovers for PCS

>>>>

### Histograms

I have a hypothesis that the longer we run through simulation, the more simulants are predicted a negative PCS value which is then clipped to a 0. Histograms over a few snapshots of time should show if this is happening.

```{r}
pcs.2021 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2021)

# pcs.2022 <- base.dat %>%
#   select(pidp, time, SF_12_PCS) %>%
#   filter(time == 2022)

pcs.2025 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2025)

pcs.2030 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2030)

pcs.2036 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2036)

merged <- rbind(pcs.2021, pcs.2025, pcs.2030, pcs.2036)
merged$time <- as.factor(merged$time)

ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
  geom_histogram() +
  labs(title = 'Distribution of SF_12_PCS')

ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
  geom_freqpoly() +
  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Count')

ggplot(merged, aes(x = SF_12_PCS, y = after_stat(density), group = time, colour = time, fill = time)) +
  geom_freqpoly() +
  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Density')
```
